---
title: "W04-02-REG-df2015na Homework"
output: html_document
---

# 문제 정답

|모형|키예측식|
|:---|:---|
|Mlm|y = 104.86782 + 5.31866gndM - 0.06027age + 0.39190wt -0.38732wa + 2.12427hdwd + 1.57590ftln - 1.08832ftwd + 0.55505bldAB - 0.31038bldB -0.13907bldO + 0.18510lftY - 0.32792smkY - 0.43018alcY |
|Mstep| y = 105.41125 + 5.27676gndM -0.06226age + 0.39174wt - 0.38821wa + 2.19044hdln + 1.49213ftln - 1.03522ftwd|


|모형| RSQ | MSE | MAE | AIC|
|:-- |:--|:--|:--|:--|
|Mlm|30.8802| 25.30651| 3.66709|645.15|
|Mstep|0.879| 21.66815| 3.601111|633.84|

|모형|gnd|age|ht|wt|wa|hdln|hdwd|ftln|ftwd|bld|lft|smk|alc|yhlm|reslm|yhstep|resstep
|:---|:---|:---|:---|:---|:---|:---|:---|:---|:---|:---|:---|:---|:---|:---|:---|:---|:---|
|본인|F|23|154|51.4|68|16|9|20|9|AB|0|0|0|153.7971|0.202867|153.2895 | 0.7105283|
|A|M|53|169|67|86|18|10.5|25|10|B|0|0|1|166.2341 | 2.765890|166.6282  |2.3718285|
|B|M|20|174|75|80|19|11|26|11|B|0|0|1|176.3076| -2.307604|176.7933 |-2.7933482|
|C|F|52|155|60|72|17.5|9|25|9.5|AB|0|0|0|164.3920 |-9.392002|163.5287 |-8.5287394|





# 패키지

```{r}
suppressWarnings(suppressMessages(library(tidyverse)))
suppressWarnings(suppressMessages(library(skimr)))
suppressWarnings(suppressMessages(library(naniar)))
suppressWarnings(suppressMessages(library(gridExtra)))
suppressWarnings(suppressMessages(library(scales)))
suppressWarnings(suppressMessages(library(dplyr)))
suppressWarnings(suppressMessages(library(caret)))
suppressWarnings(suppressMessages(library(MASS)))
```




# 읽기

```{r}
DF <- as.data.frame(read_csv('D:/Github/Statics/DataMining/0404/df2015na.csv'))
SC <- as.data.frame(read_csv('D:/Github/Statics/DataMining/0404/df2015na-sc.csv'))
```

```{r}
head(DF)
```





# 변수 조정


```{r}
sapply(DF, class)
```

```{r}
sapply(SC, class)
```

```{r}
DF <-mutate(DF,
            gnd = factor(gnd),
            bld = factor(bld),
            lft = factor(lft, labels = c('N', 'Y')),
            smk = factor(smk, labels = c('N', 'Y')),
            alc = factor(alc, labels = c('N', 'Y')))

str(DF)
```
```{r}
head(SC)
```

```{r}
SC <-mutate(SC,
            gnd = factor(gnd),
            bld = factor(bld),
            lft = factor(lft, labels = c('N')),
            smk = factor(smk, labels = c('N')),
            alc = factor(alc, labels = c('N', 'Y')))
levels(SC$lft)<-append(levels(SC$lft), 'Y')
levels(SC$smk)<-append(levels(SC$smk), 'Y')
levels(SC$bld)<-append(levels(SC$bld), c('A','O'))
str(SC)
```




# 결측
```{r}
skimr::skim(DF)
```

```{r}
naniar::miss_var_summary(DF)
```

```{r}
skimr::skim(SC)
```

```{r}
naniar::miss_var_summary(SC)
```

```{r}
DF_nomiss <- na.omit(DF)
head(DF_nomiss)
```



# 간단 탐색

```{r}
plot(DF_nomiss)
```


* 연속 ~ 연속

```{r}
R <- cor (DF_nomiss%>% select_if(is.numeric), use='pairwise.complete.obs')
R
```


```{r}
sort(R['ht', ], decreasing=TRUE)
```

```{r}
corrplot::corrplot.mixed(R, upper='ellipse', order='FPC')
```

* 이산 ~ 이산
  * 성별 흡연비율을 시각화
  * 성별 음주비율을 시각화
  * 성별 왼솝잡이비율을 시각화
  
```{r}
g1 <- ggplot(DF_nomiss, aes(x=smk, fill=gnd)) + geom_bar()
g2 <- ggplot(DF_nomiss, aes(x=alc, fill=gnd)) + geom_bar()
g3 <- ggplot(DF_nomiss, aes(x=lft, fill=gnd)) + geom_bar()

grid.arrange(g1, g2, g3, nrow=2, ncol=2)
```



# 회귀분석

### 선형회귀분석

```{r}
Mlm <- lm(ht~., data=DF_nomiss)
summary(Mlm)
```

##### Mlm 식:
y = 104.86782 + 5.31866gndM - 0.06027age + 0.39190wt -0.38732wa + 2.12427hdwd + 1.57590ftln - 1.08832ftwd + 0.55505bldAB - 0.31038bldB -0.13907bldO + 0.18510lftY - 0.32792smkY - 0.43018alcY



```{r}
par(mfrow=c(2,2))
plot(Mlm)
```

```{r}
predict(Mlm,SC)
```

```{r}
y = SC$ht
pred=predict(Mlm, SC)
resid = y-pred
cbind(y, pred, resid)
```

```{r}
MSE = sum(resid^2)/4
MAE = sum(abs(resid))/4

cat("MSE: ",  MSE, "   MAE: ", MAE)
```

##### RSQ, MSE, MAE
Rsq: 30.8802, MSE: 25.30651, MAE: 3.667091



### 변수선택 회귀분석

```{r}
Mstep <- stepAIC(Mlm)
```

```{r}
summary(Mstep)
```

##### Mstep 식:

y = 105.41125 + 5.27676gndM -0.06226age + 0.39174wt - 0.38821wa + 2.19044hdln + 1.49213ftln - 1.03522ftwd





```{r}
par(mfrow=c(2,2))
plot(Mstep)
```

```{r}
predict(Mstep, SC)
```


```{r}
y = SC$ht
pred=predict(Mstep, SC)
resid = y-pred
cbind(y, pred, resid)
```

```{r}
MSE = sum(resid^2)/4
MAE = sum(abs(resid))/4

cat("MSE: ",  MSE, "   MAE: ", MAE)
```

##### RSQ, MSE, MAE
Rsq: 0.879, MSE: 21.66815, MAE: 3.601111
